---
editor_options: 
  chunk_output_type: console
execute:
  echo: false
---

```{r}
#| label: setup


# LOAD: dat_penguins_small
dat_penguins_small <- palmerpenguins::penguins_raw[1:10, ]
```

# knitr::kable()

This is a cross-reference to @tbl-kable, rendered with the default package [knitr](https://www.rdocumentation.org/packages/knitr/versions/1.41) version `r utils::packageVersion("knitr")`.

```{r}
#| label: tbl-kable
#| tbl-cap: "knitr::kable()"

knitr::kable(dat_penguins_small)
```

# kableExtra::kable()

This is a cross-reference to @tbl-kableExtra, rendered with the package [kableExtra](https://github.com/haozhu233/kableExtra) version `r utils::packageVersion("kableExtra")`.

```{r}
#| label: tbl-kableExtra
#| tbl-cap: "kableExtra::kable()"

kableExtra::kable(dat_penguins_small)
```

# flextable::flextable()

This is a cross-reference to @tbl-flextable, rendered with the package [flextable](https://davidgohel.github.io/flextable/) version `r utils::packageVersion("flextable")`.

```{r}
#| label: tbl-flextable
#| tbl-cap: "flextable::flextable()"

flextable::flextable(dat_penguins_small)
```

# huxtable::hux()

This is a cross-reference to @tbl-huxtable, rendered with the package [huxtable](https://hughjonesd.github.io/huxtable/) version `r utils::packageVersion("huxtable")`.

```{r}
#| label: tbl-huxtable
#| tbl-cap: "huxtable::hux()"

huxtable::hux(dat_penguins_small)
```

# DT::datatable()

This is a cross-reference to @tbl-DT, rendered with the package [DT](https://github.com/rstudio/DT) version `r utils::packageVersion("DT")`.

::: {.callout-note}
Only HTML
:::

```{r}
#| label: tbl-DT
#| tbl-cap: "DT::datatable()"
if (knitr::is_html_output()) {
  DT::datatable(dat_penguins_small)
}
```

# formattable::formattable()

This is a cross-reference to @tbl-formattable, rendered with the package [formattable](https://github.com/renkun-ken/formattable) version `r utils::packageVersion("formattable")`.

```{r}
#| label: tbl-formattable
#| tbl-cap: "formattable::formattable()"

formattable::formattable(dat_penguins_small)
```

# reactable::reactable()

This is a cross-reference to @tbl-reactable, rendered with the package [reactable](https://glin.github.io/reactable/) version `r utils::packageVersion("reactable")`. [reactablefmtr](https://kcuilla.github.io/reactablefmtr/index.html) offers an extention of the syntax for styling - but not a standalone option.

::: {.callout-note}
Only HTML
:::

```{r}
#| label: tbl-reactable
#| tbl-cap: "reactable::reactable()"
if (knitr::is_html_output()) {
  reactable::reactable(dat_penguins_small)
}
```

# rhandsontable::rhandsontable()

This is a cross-reference to @tbl-rhandsontable, rendered with the package [rhandsontable](https://jrowen.github.io/rhandsontable/) version `r utils::packageVersion("rhandsontable")`.

::: {.callout-note}
Only HTML
:::

```{r}
#| label: tbl-rhandsontable
#| tbl-cap: "rhandsontable::rhandsontable()"
if (knitr::is_html_output()) {
  rhandsontable::rhandsontable(dat_penguins_small)
}
```

# pixiedust

Only works for output from the `broom` package, so not regular datasets.

# stargazer::stargazer

This is a cross-reference to @tbl-stargazer, rendered with the package [stargazer](https://cran.r-project.org/web/packages/stargazer/index.html) version `r utils::packageVersion("stargazer")`.

::: {.callout-note}
`results: asis` (i.e., creates LaTeX output)
:::

```{r}
#| label: tbl-stargazer
#| tbl-cap: "stargazer::stargazer()"
#| results: asis

stargazer::stargazer(dat_penguins_small)
```

# xtable::xtable()

This is a cross-reference to @tbl-xtable, rendered with the package [xtable](https://cran.r-project.org/web/packages/xtable/index.html) version `r utils::packageVersion("xtable")`.

::: {.callout-note}
`results: asis` (i.e., creates LaTeX output)
:::


```{r}
#| label: tbl-xtable
#| tbl-cap: "xtable::xtable()"
#| results: asis

xtable::xtable(dat_penguins_small)
```

# tangram::tangram()

This is a cross-reference to @tbl-tangram, rendered with the package [tangram](https://github.com/spgarbet/tangram) version `r utils::packageVersion("tangram")`.

::: {.callout-note}
`results: asis` (i.e., creates LaTeX output)
:::

```{r}
#| label: tbl-tangram
#| tbl-cap: "tangram::tangram()"
#| results: asis

tangram::tangram(dat_penguins_small)
```

# ztable::ztable()

This is a cross-reference to @tbl-ztable, rendered with the package [ztable](https://github.com/cardiomoon/ztable) version `r utils::packageVersion("ztable")`.

::: {.callout-error}
Could not get package to work - issue with 'list' output.
:::

```{r}
#| label: tbl-ztable
#| tbl-cap: "ztable::ztable()"
#| eval: false
tmp <- ztable::ztable(dat_penguins_small)
print(tmp)
```

# condformat::condformat()

This is a cross-reference to @tbl-condformat, rendered with the package [condformat](https://github.com/cardiomoon/ztable) version `r utils::packageVersion("condformat")`.

::: {.callout-note}
`results: asis` (i.e., creates LaTeX output)
:::

```{r}
#| label: tbl-condformat
#| tbl-cap: "condformat::condformat()"
if (knitr::is_html_output()) {
condformat::condformat(dat_penguins_small)
}
```

# pander::pandoc.table()

This is a cross-reference to @tbl-pander, rendered with the package [pander](https://rapporter.github.io/pander/) version `r utils::packageVersion("pander")`.

::: {.callout-note}
`results: markup` (i.e., creates md output)
:::

```{r}
#| label: tbl-pander
#| tbl-cap: "pander::pandoc.table()"
#| results: asis

pander::pandoc.table(dat_penguins_small)
```

# papaja::apa_table()

This is a cross-reference to @tbl-papaja, rendered with the package [papaja](https://rapporter.github.io/pander/) version `r utils::packageVersion("papaja")`.

::: {.callout-error}
`compilation failed- error Extra }, or forgotten \endgroup. l.6308 ...label{tbl-papaja}papaja::apa\_table() }}`
:::


```{r}
#| label: tbl-papaja
#| tbl-cap: "papaja::apa_table()"
#| eval: false

papaja::apa_table(dat_penguins_small)
```

# gt::gt()

This is a cross-reference to @tbl-gt, rendered with the package [gt](https://gt.rstudio.com/) version `r utils::packageVersion("gt")`.

```{r}
#| label: tbl-gt
#| tbl-cap: "gt::gt()"

gt::gt(dat_penguins_small)
```
